Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
Fleshed out abstract

We present a scalable method for Gaussian Process regression in one dimension
with a specific emphasis on large astronomical time-series data sets.
This method can be applied to any Gaussian Process model where the spectral
density can be expressed as any general mixture of damped sinusoid functions.

>>>>

We present a scalable method for Gaussian Process regression in one dimension
with a specific emphasis on large astronomical time-series data sets.
This method, which we christen \celerite, can be applied to any Gaussian Process model where the spectral
density can be expressed as any general mixture of damped sinusoid functions.
We present a mathematical description of \celerite,
its relation to the stochastically-driven, damped simple harmonic oscillator, 
and details of the implementation.  We give examples of \celerite\ applied to both 
simulated and actual astronomical time-series, using it to estimate the time-series
power spectrum, while simultaneously accounting for correlated noise when inferring 
model parameters.  These examples include Bayesian estimation of the strength 
of stellar granulation, stellar rotation periods, asteroseismic spectra, and 
transiting planet light curve parameters.  The model is flexible, fast, and 
general, with potential for application to a wide range of astronomical problems, 
for which we provide open-source software that implements \celerite\ in 
\project{C++}, \project{Python}, and \project{Julia}.
